\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-30 paper.tex
moved figures and added comments
more info about git methodology

% TODO this whole section should probabyl be in the appendix
\section{Version Control}
\label{sec:versionControl}

@@

Some members of our team were very excited by the workflows GitHub's tools
enabled.

@@

@@

One idea that was proposed initially was an AR audio experience using 3D
spatialized audio. Instead of traditional AR where the user is constantly
looking through the camera, this experience would allow users to keep their
phones in their pockets while taking the tour. Sound sources would change in
relation to the real world as the user moved around.

@@

Despite these issues our team is happy with the product we delivered to
Kyoto~VR. ARuko is not quite ready to be sold on app stores yet, but with a
little more development time it could easily be completed. The UI could use
more testing with real users to make sure it is intuitive and easy to use. We
also intended to add a feature where the app could automatically download tour
files from the Editour server and import them without having to rebuild. We were
not able to complete this feature due to time constraints, but it could easily
be added because all of ARuko's business logic is abstracted and generalized to
support multiple tours. Editour also already supports requesting and downloading
the most recent versions of tours.

>>>>

% TODO this whole section should probably be in the appendix
\section{Version Control}
\label{sec:versionControl}

@@

Some members of our team were very excited by the workflows GitHub's tools
enabled. In this section, we will discuss some of the tools, some of which
greatly aided in our organization and productivity.

@@

% TODO give this paragraph some more context so it doens't seem out of place
The way we incorporated branches into our workflow helped us collaborate in a
way that kept us organized. In general, if one of us was working on a specific
feature, we would create a branch with a name descriptive of that feature. This
methodology minimized difficult-to-resolve merge conflicts.
% TODO explain merge conflicts and cite that Atlassian thing

Once we deployed Editour to a server so that Atticus could begin to use it,
we changed the version to v1.0.0 to indicate the first release version. At this
point, it was important that the master branch remain as stable as possible.
Because of this, we created a ``dev'' branch where we could test experimental
features to improve the experience and functionality of Editour. Maintaining a
stable and experimental branch reduced the risks involved with continuing to
iterate on the software's features post-release.

In a similar vein, with ARuko we used branches to ensure we had a stable working
version. The night before field testing at Kinkaku-ji, we would cease work on
the most recent branch, and build the app to our phones. This way, we would
always have an exact snapshot of the code we used for that day of testing.

@@

% TODO is spatialized really a real word or do people just use it?
One idea that was proposed initially was an AR audio experience using 3D
spatialized audio. Instead of traditional AR where the user is constantly
looking through the camera, this experience would allow users to keep their
phones in their pockets while taking the tour. Sound sources would change in
relation to the real world as the user moved around.

@@

Despite these issues our team is happy with the product we delivered to
Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
project, but we were able polish the app enough such that it would be feasible
for Atticus to eventually sell the app. The UI could use more testing with real
users to make sure it is intuitive and easy to use. We also intended to add a
feature where the app could automatically download tour files from the Editour
server and import them without having to rebuild. We were not able to complete
this feature due to time constraints, but it could easily be added because all
of ARuko's business logic is abstracted and generalized to support multiple
tours. Editour also already supports requesting and downloading the most recent
versions of tours.
